A Two-Infall Star Formation History with Outflows and Radial Migration

### 2025-01-09 src/tex/ms.tex
Updates from Overleaf
Manuscript updates

\begin{figure*}
    \centering
    \includegraphics{figures/onezone_params.pdf}
    \caption{Caption.}
    \label{fig:onezone-params}
\end{figure*}

\begin{figure}
    \centering
    \includegraphics{figures/yield_outflow.pdf}
    \caption{Caption.}
    \label{fig:onezone-dtd}
\end{figure}

>>>>

\begin{figure*}
    \centering
    \includegraphics{figures/onezone_params_low_yields.pdf}
    \caption{Illustration of the effect of changing the infall history parameters on one-zone gas-phase abundances.}
    \label{fig:twoinfall-parameters-low-yields}
\end{figure*}

% \begin{figure*}
%     \centering
%     \includegraphics{figures/onezone_params_high_yields.pdf}
%     \caption{Caption.}
%     \label{fig:twoinfall-parameters-high-yields}
% \end{figure*}

\begin{figure}
    \centering
    \includegraphics{figures/yield_outflow.pdf}
    \caption{Key takeaway: the higher yields produce slower recent evolution of [O/H] and [Fe/H], but a greater rise in [O/Fe] after the second infall. In contrast, the lower yields lead to a more rapid evolution of [O/H] and [Fe/H], but a much smaller rise in [O/Fe].}
    \label{fig:onezone-dtd}
\end{figure}
